% Welcome to the simple Undergraduate Complexity Research CV-resume template!
% Please delete any sections that do not apply to your past experiences. We do not expect that applicants will have itmes for all of the sections included here. You can also rename or revise sections to best fit with your personal accomplishments.

\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{blindtext}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage{baskervillef}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\setlength{\footskip}{10pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{0.0in}
\addtolength{\evensidemargin}{0.0in}
\addtolength{\textwidth}{0.0in}
\addtolength{\topmargin}{0.2in}
\addtolength{\textheight}{0.0in}


\urlstyle{same}

%\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \it\vspace{3pt}
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}


\begin{center}
    {\LARGE{Ishaan Shrivastava}} \\ \vspace{0pt}
    \begin{multicols}{2}
    \begin{flushleft}
    \large{Uttar Pradesh, Noida} \\
    \large{201304} \\
    \end{flushleft}
    
    \begin{flushright}
% this could be LinkedIn, GitHub, or a personal website or social media account (if used for professional purposes)
    \href{https://github.com/shrivastava95}{\bf\underline{Github}}
    \href{https://www.linkedin.com/in/ishaanshri95/}{\bf\underline{LinkedIn}}
    \href{https://codeforces.com/profile/ishaanshri95}{\bf\underline{Codeforces}}
    \\
% please ensure your email address is one you check
    \href{mailto:shrivastava.9@iitj.ac.in}{\bf{shrivastava.9@iitj.ac.in}}
    \end{flushright}
    \end{multicols}
\end{center}


%-----------EDUCATION-----------
% Please list your current institution first and then past schools in reverse chronology. No need for GPA, etc. You do not need to include high school but may do so if there are accomplishments you would like to highlight.
\section{Career Summary}


My current objective is to make vision-language models learn how to reason better for less. Machine-Learning Engineer, published paper on multimodal vision-language models (“Learn ‘No’ to Say ‘Yes’ Better”) cited 30 times, rated among the top 7\% of competitive programmers on codeforces, ranked number 1 on the \href{https://www.tensortonic.com/}{tensortonic} leaderboard. Working on multimodal VLMs and shipping computer vision solutions on a variety of tasks at Metafusion.

% I am also interested in working inside open-source ecosystems to utilize my understanding of algorithms and further refine/develop open-source software related to popular growing libraries in Python, and work on projects related to the same.


%-----------SKILLS-----------
\section{Skills and Technologies}
% This section can include programming or spoken languages, text editing and general software knowledge, certifications, version control or project management tools, or other skills that might be relevant. You can include as many or as few as you like: delete or add as needed.  
\begin{itemize}[leftmargin=0.15in, label={}]
    \normalsize{\item{
     \textbf{Programming Languages}{: Python (4+ years), C++/C (4+years), MATLAB, Git} \\
     \textbf{Open-source libraries}{: PyTorch, Jax, einops, Numpy, OpenCV, Pillow} \\
    }}
 \end{itemize}


\section{Coursework}
% This section can include programming or spoken languages, text editing and general software knowledge, certifications, version control or project management tools, or other skills that might be relevant. You can include as many or as few as you like: delete or add as needed.  
% \begin{itemize}[leftmargin=0.15in, label={}]
%     \normalsize{\item{
%      \textbf{AI and Data Science}{: \\
%      CSL2050 Pattern Recognition and Machine Learning, CSL4030 Data Engineering, CSL4010 Optimization for Machine Learning, CSL7610 Artificial Intelligence} }\item{
%      \textbf{Computer Science}{: \\CSL1010 Intro to Computer Science, CSL2020 Data Structures and Algorithms, CSL2080/CSL2090 Principles of Computer Systems I \& II (Operating Systems and Networking)}} \item{
%      \textbf{Mathematics}{: \\MAL1010/MAL1020 Mathematics I \& II, MAL2010 Probability, Statistics and Stochastic Processes}}
%     }
%  \end{itemize}

\begin{multicols}{3}
\textbf{{AI and Data Science}}
\begin{itemize}
\itemsep0em 
    \item{Pattern Recognition and Machine Learning}
    \item{Data Engineering}
    \item{Artificial Intelligence}
    \item{Advanced Artificial Intelligence}
    \item{Deep Learning}
    \item{Dependable AI}
\end{itemize}
\columnbreak
\textbf{{Mathematics}}
\begin{itemize}
\itemsep0em 
    \item{Probability, Statistics and Stochastic Processes}
    \item{Mathematics I \& II}
    \item{Optimization for Machine Learning}
    \item{Introduction to Game Theory}
    \item{Introduction to Financial Engingeering}
\end{itemize}
\columnbreak
\textbf{{Computer Science}}
\begin{itemize}
\itemsep1em 
    \item{Intro to Computer Science}
    \item{Data Structures and Algorithms}
    \item{Principles of Computer Systems I \& II (Operating Systems and Networking)}
\end{itemize}

\end{multicols}


%-----------PUBLICATION EXPERIENCE-----------
\section{Publications}
% it is not expected that applicants have research experience but this section can include experience gained in a laboratory course, shadowing experiences, or group or independent research projects
\resumeSubHeadingListStart

\resumeSubheading
        {Learn ``No'' to Say ``Yes'' Better: Improving Vision-Language Models via Negations}{\href{https://arxiv.org/abs/2403.20312}{- \textit{\underline{arXiv preprint}}}}
        {Jaisidh Singh$^*$, \textbf{Ishaan Shrivastava$^*$}, Mayank Vatsa, Richa Singh, Aparna Bharati}{\href{https://openaccess.thecvf.com/content/WACV2025/html/Singh_Learning_the_Power_of_No_Foundation_Models_with_Negations_WACV_2025_paper.html}{Published - \textit{\underline{WACV2025}}}}

\resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{Work Experience}
% it is not expected that applicants have research experience but this section can include experience gained in a laboratory course, shadowing experiences, or group or independent research projects
\resumeSubHeadingListStart

\resumeSubheading
        {Computer Vision Research Engineer}{May '24 -- Current}
        {Metafusion [Supervisor: Manish Soni]}{Noida, India}
      \resumeItemListStart
        \resumeItem{Curated 20+ benchmarks for object detection and performed ablations, boosting narrow-domain performance over SOTA by 2\% and yielding an improved pretrained object detection base for downstream finetuning.}
        \resumeItem{Independently discovered a \textbf{data-free structured pruning} method for attention-layer skipping in VLMs by leveraging insights from \textbf{heavy-tailed self-regularization theory (HTSR)}}
        \resumeItem{Research and development of a person-attribute recognition pipeline resistant to distribution shifts. Successfully deployed across many different applications.}
        \resumeItem{Optimisation and backend fixes for \textbf{Multi Object Tracker (MOT)}, leading to an average of 12-15\% performance increase over a wide range of MOT metrics.}
        \resumeItem{Development and maintenance of \textbf{FuseNets}, a deep-learning library created to accelerate and automate the R\&D and deployment of novel computer vision model architectures on detection, segmentation, and recognition.}
        \resumeItem{Responsible for training and deploying a variety of \textbf{I3d feature}-based approaches for person attribution and violence detection on low quality video surveillance feeds in low data conditions.}
    \resumeItemListEnd

\resumeSubheading
        {Open source engineer}{May '23 -- Aug '23}
        {CodeForGovTech '23 [Supervisor: Gautam Rajeev] }{Remote}
      \resumeItemListStart
        \resumeItem{Devised and implemented a low-cost framework for improving translations in transformer-based models using a dictionary of translations.}
        \resumeItem{Improved google's \textbf{Tesseract OCR} performance on multilingual document parsing using \textbf{OpenAI's CLIP} and published multiple open source libraries for further development and refinement around the same.}
        \resumeItem{Worked with supervisors for \textbf{successful deployment} of multilingual parser, positively impacting \textbf{millions of farmers in underrepresented} and underprivileged language communities.}
    \resumeItemListEnd

\resumeSubheading
        {Undergraduate researcher}{May '23 -- Aug '23}
        {Supervisor: Dr. Shweta Jain }{Ropar, Punjab, India}
      \resumeItemListStart
        \resumeItem{Worked on improving fairness in non-i.i.d federated classification settings using knowledge distillation, EMA, and stochastic weight averaging.}
        \resumeItem{Implemented the \textbf{Ditto} framework for federated learning in PyTorch and ran experiments on it.}
        \resumeItem{Achieved an improvement of 0.2\% upon other baselines.}
    \resumeItemListEnd

% \resumeSubHeadingListEnd



% %-----------RESEARCH EXPERIENCE-----------

% \section{Other Experience}
% % it is not expected that applicants have research experience but this section can include experience gained in a laboratory course, shadowing experiences, or group or independent research projects
% \resumeSubHeadingListStart

\resumeSubheading
        {AI researcher}{Dec '22 -- Feb '23}
        {MURVEN [Supervisor: Murugan Venugopal]}{Chennai, Tamil Nadu, India}
      \resumeItemListStart
        \resumeItem{Analysis, design, coding, integration, debugging and deployment of diffusion models using AI to prompt the generation of video animations}
        \resumeItem{Working on a reusable and intuitive framework for prompting \textbf{Stable Diffusion} to generate animations}
    \resumeItemListEnd

\resumeSubheading
        {Computer Vision Engineer Intern}{Nov '22 -- Feb '23}
        {QwizPad [Supervisor: Mohit Shrivastava]}{Chandigarh, Punjab, India}
      \resumeItemListStart
        \resumeItem{Integrated a digit recognition model into existing digital evaluation framework in \textbf{.NET} using inter-process communication}
        \resumeItem{eliminated disk read-writes to enable very high speed scanning and inference of OMR sheets}
    \resumeItemListEnd


\resumeSubheading
        {Undergraduate researcher}{Jan '22 -- Jul '22}
        {Supervisor: Dr. Angshuman Paul }{Jodhpur, Rajasthan, India}
      \resumeItemListStart
        \resumeItem{Worked on highly imbalanced fine grained spine and chest x-ray image classification on \textbf{VinDr-SpineXR} and \textbf{VinDr-PCXR} datasets}
        \resumeItem{Developed a general - purpose class-incremental learning pipeline with \textbf{Knowledge Distillation} and \textbf{DenseNet}}
        \resumeItem{Set a baseline for further class incremental learning research in this area}
    \resumeItemListEnd
    

\resumeSubHeadingListEnd


%-----------OTHER EXPERIENCE-----------
\section{Projects}
% if you have been employed, do volunteer activities, or have held other formal or informal jobs, you can list them here.   
\resumeSubHeadingListStart
    \resumeSubheading
        {DevRev Expert Answers in a Flash: \newline Improving Domain-Specific QA - \href{https://colab.research.google.com/drive/1_fuSPJtwWz5JTKI-_aouqvkXWD-MwKDP?usp=sharing}{\bf\underline{Colab}}}{Dec '23 -- Jan '23}
        {Supervisor: Self Project}{}
        \resumeItemListStart
            \resumeItem{Implemented a Document retrieval and extractive question answering pipeline using pre-trained LLMs in Low-resource settings without GPU.}
            \resumeItem{Reduced overall pipeline inference time (document retrieval from an corpus of data + extractive QA) to under 700 ms per query.}
            \resumeItem{Conducted an extensive ablation study of approached used in order to push the inference time and evaluation metrics.}
        \resumeItemListEnd
        
    \resumeSubheading
        {Self-Supervised robust Adversarial Attack Detection - \href{https://github.com/shrivastava95/dependable-ai/tree/main/Minor_1}{\bf\underline{Github}}}{Jan '23 -- Jan '23}
        {Supervisor: Prof. Richa Singh, Prof. Mayank Vatsa, CSL7370 (Dependable AI)}{}
        \resumeItemListStart
            \resumeItem{Implemented an Autoencoder to maximise the reconstruction error of adversarially attacked samples by implementing a self-supervised triplet loss objective by mimicing the behaviour of attacked samples.}
            \resumeItem{Reproduced results on the original datasets as well as new ones mentioned in the original paper.}
        \resumeItemListEnd
    

        
    \resumeSubheading
      {FRUITS-360 classifier web-app - \href{https://github.com/sawmill811/Fruits360}{\bf\underline{Github}}}{March '22 -- May '22}
      {Supervisor: Prof. Richa Singh, CSL2050 (Pattern Recognition and Machine Learning)}{}
      \resumeItemListStart
        \resumeItem{Explored a wide variety of ML algorithms - Decision trees, Random
Forest, XGBoost / LightGBM, SVMs, MLP}
        \resumeItem{Made a pipeline for classifying fruit images trained on Fruits-360 data.}
        \resumeItem{Hosted a webpage with a fine-tuned VGG16-based model as backend}
        \resumeItemListEnd

    \resumeSubheading
      {Flight price prediction}{March '22 -- April '22}
      {Supervisor: Prof. Richa Singh, CSL2050 (Pattern Recognition and Machine Learning)}{}
      \resumeItemListStart
        \resumeItem{Used the google API to gather Google Trends data on festivals to improve flight
price prediction}
        \resumeItem{Tested various machine learning approaches - SFS, decision tree regressors, etc.}
        \resumeItem{Made and deployed a pipeline of ensemble models trained on the provided dataset.}
        \resumeItemListEnd

\resumeSubHeadingListEnd

% %-----------AWARDS & HONORS-----------
% \section{Awards \& Honors} 
% % This section can include academic achievements – things like scholarships, Dean's list, honors societies – as well as recognition in your community - community service, religious study, volunteerism, military service, or anything else. You can remove or add sections as needed.
% \resumeSubHeadingListStart
%     \resumeSubheading
%     {Title or brief description of the award}{}
%     {University, Sponsor or Organization}{year(s)}
%     \resumeSubheading
%     {Title or brief description of the award}{}
%     {University, Sponsor or Organization}{year(s)}
%     \resumeSubheading
%     {Title or brief description of the award}{}
%     {University, Sponsor or Organization}{year(s)}
% \resumeSubHeadingListEnd



 
%-----------Relevant coursework and certifications-----------

\section{Education}
\resumeSubHeadingListStart

    \resumeSubheading
        {Indian Instititue of Technology, Jodhpur (present)}{November '20 -- May '24}
        {B.Tech in Artificial Intelligence and Data Science - current CGPA 8.1 / 10}{Jodhpur, Rajasthan, India}
      \resumeSubheading
        {Stepping Stones Sr. Secondary School}{March '18 -- Feb '20}
        {Central Board of Secondary Education - CGPA 8.96 / 10}{Chandigarh, Punjab, India}
      \resumeSubheading
        {Strawberry Fields High School}{March '07 -- Feb '18}
        {Council For The Indian School Certificate Examinations - CGPA 8.3 / 10}{Chandigarh, Punjab, India}

\resumeSubHeadingListEnd







%-----------PORS-----------
\section{Positions of Responsibility}
% Also an optional section, for any hobbies, sports, artistic and musical pursuits, etc. that you would like to include. You can include as many or as few as you like: delete or add as needed. 
\resumeSubHeadingListStart
    \resumeSubheading
      {Core Member - Programming Club, IIT Jodhpur}{August '22 -- May '24}
      {}{}
      \resumeItemListStart
        \resumeItem{Problemsetter for Programming Club's monthly competitive programming contest, Dinnertime, and IIT Jodhpur's Tech Fest, Prometeo}
        \resumeItem{Inculcated programming culture and interest for competitive programming among the community}
        \resumeItemListEnd

\resumeSubHeadingListEnd

 
%-----------Relevant coursework and certifications-----------
\section{Achievements}
% This section can include programming or spoken languages, text editing and general software knowledge, certifications, version control or project management tools, or other skills that might be relevant. You can include as many or as few as you like: delete or add as needed.  
\begin{itemize}[leftmargin=0.15in, label={}]
     \item{
     \textbf{Expert at Codeforces}{ Reached ‘Expert’ (rating 1749, 7 months, 33 contests) – top 7 \% on Codeforces}}
\end{itemize}


%-----------Other interests-----------
\section{Other Interests}
% Also an optional section, for any hobbies, sports, artistic and musical pursuits, etc. that you would like to include. You can include as many or as few as you like: delete or add as needed. 
\begin{itemize}[leftmargin=0.15in, label={}]
    \normalsize{
        \item{Avid chess player, origami enthusiast, and active competitive programmer (Codeforces 'Expert'). I thrive under competition.}
    }
 \end{itemize}
\end{document}
